\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2010-07-23 article.tex
Rewording of the intro to the data section

  Our data comes from two different sources. The terminology associated with
  movements are from Taekwon-Do ITF Sonkal Praha\footnote{\url{http://sonkal.taekwondo.cz}},
  and the English description of each movement is from the condensed
  encyclopedia\cite{cyclo:con}.

  The terminology dataset is organized by pattern names. It contains a list of
  all techniques in patterns Chon-Ji to Juche using terminology. It also
  includes motion type on movements that are not performed in normal motion.
  The file was reviewed and minor corrections were made to the terminology.

@@

% added English movement description from the condensed encyclopedia
% added tags
%   give an overview over (groups of) tags, see movements_with_tags.txt
%     Group of tags
%     Groups of techniques {blocks, strikes, thrusts, punches}
%       height
%       weapon
%       type etc.
%   show an example (chon-ji movement no. 1, for instance)
% divided each pattern into its own text file (./patterns/*)
% modelled the project in the database (./models)
%   explain all attributes etc.
% made a ruby script to parse the text files (link to bootstrap.rb ?)
%   adding the contents into a database using datamapper (orm) (link to datamapper) || populated the database using Datamapper (orm)
%   saving the data into an sqlite3 database for analysis
%

>>>>

  Our data comes from two different sources. The terminology associated with
  pattern movements is from Taekwon-Do ITF Sonkal Praha\footnote{\url{http://sonkal.taekwondo.cz}},
  and the English description of each movement is from the condensed
  encyclopedia\cite{cyclo:con}.

  The terminology dataset is organized by pattern names. It contains a list of
  all techniques in patterns Chon-Ji to Juche using terminology. It also
  includes motion type on movements that are not performed in normal motion.

  The English description to every movement was registered manually after
  reviewing, and making minor corrections to, the terminology.

@@

% added tags
%   give an overview over (groups of) tags, see movements_with_tags.txt
%     Group of tags
%     Groups of techniques {blocks, strikes, thrusts, punches}
%       height
%       weapon
%       type etc.
%   show an example (chon-ji movement no. 1, for instance)
% divided each pattern into its own text file (./patterns/*)
% modelled the project in the database (./models)
%   explain all attributes etc.
% made a ruby script to parse the text files (link to bootstrap.rb ?)
%   adding the contents into a database using datamapper (orm) (link to datamapper) || populated the database using Datamapper (orm)
%   saving the data into an sqlite3 database for analysis
%
